\documentclass[]{adamyi-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\revision{3}

\header{Adam}{Yi}{full-stack developer, white hat hacker and independent researcher}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
~
+86 186-1071-3116
+1 (402) 417-0115
+1 (716) 666-0115
~
\href{mailto:i@adamyi.com}{i@adamyi.com}
\href{https://www.yiad.am}{http://www.yiad.am}
\section{education}
2012-2018 Beijing 101 Middle School
\section{programming}
C, C++, PHP
Java, Golang, Python
Kotin, JavaScript
CSS3 \& HTML5
\versionsection
\end{aside}

%----------------------------------------------------------------------------------------
%	CS SECTION
%----------------------------------------------------------------------------------------

\section{computer science}

\begin{entrylist}

%------------------------------------------------

\entry
{MUNPANEL}
{Jun. 2016 -- Present}
{\emph{Founder \& Chief Technology Officer}
\begin{itemize}
\item Came up with the idea to design a Model UN platform that connects all conferences, clubs, and MUNers together.
\item Led a team of 4 members to develop and run the Model UN platform, which has 2 conferences, 100+ schools, and 2,000+ users so far, with 500+ maximum DAU (daily active users).
\end{itemize}}

%------------------------------------------------

\entry
{White Hat Hacker}
{Feb. 2015 -- Present}
{\begin{itemize}
\item Discovered more than 10 vulnerabilities of some large companies, like GlobalCash, a prepaid MasterCard provider in Hong Kong, Apple Inc, etc.
\item Got 4,000 CNY award and a Huawei Smart Bracelet for free due to a 0-day vulnerability of eYou, the email software provider for many large corporations and government departments including the Office of State Council, I discovered.
\end{itemize}}

%------------------------------------------------

\entry
{Google}
{Jun. 2016 -- Present}
{\emph{Translator}
\begin{itemize}
\item Volunteered to help translating English subtitles of keynotes and sessions of Google I/O 2016 and 2017 into Chinese for YouTube viewers and Study Jams groups.
\item Got invited by Google DevRel to Google Beijing Office and as community partner to Google I/O 2017 in San Jose.
\end{itemize}}

%------------------------------------------------

\entry
{Chaoli Forum}
{Nov. 2014 -- May. 2015}
{\emph{Co-Founder \& Developer}
\begin{itemize}
\item Developed functions like documents uploading, CDN integration, customer feedback, etc. based on esoTalk, a no-longer maintained open source forum program, as a member of the initial development team and founding team of Chaoli forum, a forum for Math, Physics, Chemistry, and Informatics lovers, which now has 5,000+ users and 40,000+ threads.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	MODEL UN SECTION
%----------------------------------------------------------------------------------------

\section{model un}

\begin{entrylist}

%------------------------------------------------

\entry
{Beijing 101 Middle School Model UN Club}
{Aug. 2016 -- Aug. 2017}
{\emph{Management Board Member}
\begin{itemize}
\item Attended more than 10 conferences in China as either delegate, academic team member, or organizing team member.
\item Managed all the things inside the club as well as outside the club, which is the second largest club in Beijing 101 Middle School, together with 10 other students.
\item Designed classes to teach new club members key Model UN skills such as game theories.
\end{itemize}}

%------------------------------------------------

\entry
{Beijing Model United Nations Association for High School Students}
{Aug. 2016 -- Aug. 2017}
{\emph{Director of Academics (English)}
\begin{itemize}
\item Managed the largest Model UN association consisting of 60+ member schools together with 12 other organizing team members.
\item Cooperated with my partner to take charge of all facets of English committees in two largest Model UN conferences for high school students in Beijing, such as reviewing academic design, background guide, etc.
\item Run the www, email, ns \& git server of the association.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\pagebreak


%----------------------------------------------------------------------------------------
%	RESEARCH SECTION
%----------------------------------------------------------------------------------------

\section{research}

\begin{entrylist}

%------------------------------------------------

\entry
{MessageOnTap \& PersonalGraph}
{Dec. 2016 -- Present}
{\emph{Researcher}
\begin{itemize}
\item Developed a framework for personal-data-powered messaging assistants and a semantic-structured graph database for mobile personal data, which will be open sourced in a few months, together with three other researchers and 8 research assistants under the supervision of Professor Jason Hong at CHIMPS Lab, Human-Computer Interaction Institute, Carnegie Mellon University.
\end{itemize}}

%------------------------------------------------

\entry
{A New Type of Catkin Collecting Device}
{Jun. 2015 - Oct. 2016}
{\emph{Independent Researcher}
\begin{itemize}
\item Built a catkin collecting device to deal with the severe air pollution – to be specific, catkins flying in the air – in China on my own.
\item Won the second prize of the 16$^{th}$ Awarding Program for Future Scientists, and 20,000 CNY as an award together with the prize.
\end{itemize}}

%------------------------------------------------

\entry
{A New Type of Fast Particulate Matter Detector}
{Jul. 2014 - Apr. 2015}
{\emph{Independent Researcher}
\begin{itemize}
\item Built a new type of particulate matter detector capable of detecting particulate matters under different diameters in different environments or on different surfaces using the light scattering method on my own.
\item Won the gold medal of 43$^{th}$ International Exhibition of Inventions of Geneva as well as a special award from Taiwan.
\item Having an invention patent under application process (CN105486617A).
\end{itemize}}

%------------------------------------------------

\end{entrylist}



%----------------------------------------------------------------------------------------
%	SCHOOL SECTION
%----------------------------------------------------------------------------------------

\section{school activities}

\begin{entrylist}

%------------------------------------------------

\entry
{Beijing 101 Middle School Student Union}
{Oct. 2012 -- Present}
{\emph{Director of Technology Department}
\begin{itemize}
\item Helped coordinate and check daily affairs of the whole grade as a member of the General Affairs Department of the Student Union of the grade from 2012 to 2015.
\item Helped selling school souvenirs like bear and alpaca toys in school uniform, as a member of the Liaison Department of the School Student Union in 2016.
\item Coordinated with the student union of other schools in Beijing to organize several large inter-school events like the inter-school Christmas Express.
\item Elected as the founding vice director of the newly established Technology Department in October 2016 and became the director later.
\item Recruited 2 extra members for the Technology Department and organized several tech-related events in school, such as the School Science Festival together.
\item Provided Wi-Fi support for several important events in school on my own, such as the Adult Ceremony for senior students.
\end{itemize}}

%------------------------------------------------

\entry
{TEDxYouth@Beijing101}
{Jun. 2014 -- Present}
{\emph{Technology Supervisor}
\begin{itemize}
\item Managed tech-related devices like the HDMI Matrix Switch and timer of TEDxYouth@Beijing101 2014 as the only freshman volunteer, and did the same thing in 2015.
\item Co-organizing the next TEDxYouth@Beijing101 event as the technology supervisor, taking charge of all tech-related facets.
\end{itemize}}

%------------------------------------------------

\end{entrylist}


\end{document}
