\documentclass[hidelinks__VERSION__]{adamyi-cv} 

\begin{document}

\revision{__REVISION__}
\footertext{This version was compiled on \today\ at \DTMcurrenttime. Source code available at \href{https://github.com/adamyi/cv}{https://github.com/adamyi/cv} under MIT license.}

\header{Adam}{Yi}{Software/Security Engineer interested in infrastructure, enthusiastic researcher/developer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
Clickable links are red
\section{contact}
+61 4 3207 0150
+1 (808) 278-0103
+86 186 1071 3116
~
\href{mailto:i@adamyi.com}{i@adamyi.com}
\href{https://www.adamyi.com}{https://adamyi.com}
~
\href{https://github.com/adamyi}{github.com/adamyi}
\small\href{https://linkedin.com/in/adam-yi}{linkedin.com/in/adam-yi}
\href{https://git.yiad.am}{https://git.yiad.am}
\section{programming}
~
C/C++, PHP
Python, Java, Golang
Objective-C, Matlab
\LaTeX, Shell, SQL
JavaScript
CSS3 \& HTML5
\versionsection
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{https://unsw.edu.au}{University of New South Wales}, Sydney Australia}
{Jul. 2018 -- May. 2021}
{\emph{\textbf{B.S.} in Computer Science}\\
Comp-Sci course WAM (Weighted Average Mark): 98/100 HD (High Distinction)\\Cum. WAM: 91/100 HD\\
Relavent courses: \emph{Data Structures and Algorithms} (99/100 HD), \emph{Extended Web Application Security and Testing} (100/100 HD), \emph{Database Systems} (100/100 HD), \emph{System and Software Security Assessment (COMP6447/9447)} (unofficial student)\\
Currently taking: \emph{Cyber Security Project}, \emph{Web Data Compression and Search}, \emph{Extended Algorithms and Programming Techniques}\\
\href{https://drive.google.com/file/d/1Ntpk90ChuyKeYaIsLXnpJiXGrVlyAPxI/view}{Click here to view academic statement}
}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{http://cmuchimps.org/}{CHIMPS Lab}, \href{https://www.hcii.cmu.edu/}{Human-Computer Interaction Institute}, \href{https://www.cmu.edu/}{Carnegie Mellon University}}
{Dec. 2016 -- Oct. 2018}
{\emph{Research Assistant}
\begin{itemize}
\item Co-developed an early prototype of \href{https://github.com/MessageOnTap}{MessageOnTap}, an Android framework to facilitate smart pop-ups based on user's instant messages, instructed by PhD candidate \href{mailto:fanglin@cmu.edu}{Fanglin Chen}
\item Designed and implemented the core extensible architecture of the early prototype of MessageOnTap, that would allow developers to extend the framework by developing their own plugins, and was in charge of \href{https://github.com/MessageOnTap/MessageOnTap_API}{MessageOnTap API}, its IPC library for communicating between plugins and core.
\item Developed \href{https://github.com/adamyi/CrowdAnnotator}{an online system} and hired 2,500+ Amazon mTurk workers to annotate sensitive information in 65,000+ pieces of data for us to train a PII (Personally Identifiable Information) scrubbing algorithm (DeepScrub).
\item Trained a \href{https://github.com/adamyi/Word2Vec_Reddit}{Word2Vec model with Reddit corpus} to predict apps user might use.
\item Run the internal Git, Maven \& Jenkins server used by our team.
\item Called by colleagues "strong developer with creative ideas" and "more intelligent and mature than many graduate students" in \href{https://web.archive.org/web/20190612011924/https://webcache.googleusercontent.com/search?q=cache:bhkkXtbnDPQJ:https://gaoliyao.github.io/report2017.html&hl=en}{Liyao's blog post} and \href{https://drive.google.com/file/d/1uW6ZahNYufCw7_nEwLBAYFibuD5-7JBd/view}{Fanglin's recommendation}
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{Honorable Mention}
{Oct. 2018}
{\emph{\textbf{ACM-ICPC South Pacific Regional Sydney Site}}\\
Team of 3, solved half of the questions without any prior training.
}

%------------------------------------------------

\entry
{Second Place}
{Oct. 2018}
{\emph{\textbf{Cyber Security Challenge Australia (CySCA)}}\\
\href{https://www.cyberchallenge.com.au/}{CySCA} is Australia’s only national cybersecurity competition (CTF), run by The Federal Government’s Australian Cyber Security Centre and AustCyber, Telstra, PwC, Cisco, Microsoft, Commonwealth Bank, Splunk, BAE Systems, and HackLabs. I participated in UNSW3, a team of 4 students, and got the second place among 109 teams across Australia (427 students). The award includes flights to Canberra for award ceremony at Australian Signals Directorate office, flights and accommodation to Kiwicon 2018 in Wellington, New Zealand, and a Pixel 3 XL 128GB.
}

%------------------------------------------------

\entry
{First Place}
{Aug. 2018}
{\emph{\textbf{UNSW Security Society Capture the Flag}}\\
It's UNSW Security Society's largest internal CTF competition. In a team of two first-time CTF players, we got first place out of 30 teams.
}

%------------------------------------------------

\entry
{Gold Medal}
{Apr. 2015}
{\emph{\textbf{International Exhibition of Inventions of Geneva}}\\
The exhibition was organized by the Swiss Federal Government, during which I received a gold medal for designing a particulate matter detector using the light scattering method during junior/middle school. During the exhibition, I also received a Special Award from the \href{http://www.tia-tw.net/}{Taiwan Invention Association}.
}

%------------------------------------------------

\end{entrylist}

% \pagebreak

%----------------------------------------------------------------------------------------
%	ORGANIZATIONS SECTION
%----------------------------------------------------------------------------------------

\section{organizations}

\begin{entrylist}

%------------------------------------------------

\entry
{\href{https://www.munpanel.com}{MUNPANEL}}
{Nov. 2016 -- Jul. 2017}
{\emph{Founder \& Chief Technology Officer}
\begin{itemize}
\item Led a team of 4 members to develop and run an online Model United Nations platform to digitalize how high school MUN works in China, which has served 3 conferences, 170+ registered schools, and 2,000+ registered users, with 500+ max DAU (daily active users), 235,000+ total visits and 490,000+ CNY cash flow till July 2017.
\end{itemize}}

%------------------------------------------------

\entry
{White Hat Hacking (Ethical Hacking/Cybersecurity Research)}
{Feb. 2015 -- Present}
{\begin{itemize}
\item Discovered 10+ vulnerabilities in various bug bounty programs like Atlassian's.
\item Discovered a zero-day vulnerability in \href{https://www.eyou.net/}{eYou.net}, one of the two most widely-used email server software in China, used by the Government and many Chinese corporations.
\end{itemize}}

%------------------------------------------------

\entry
{Google Developers Community Programs (Beijing)}
{Jun. 2016 -- May. 2018}
{\emph{Translator (Volunteer)}
\begin{itemize}
\item Translated English subtitles of Google Developer videos including I/O keynotes into Chinese for official Youtube, Youku and Bilibili.
\item Invited to Google I/O in Mountain View as a Community Partner.
\item Reviewed and translated some of Google's official blog posts and announcements before releasing.
\item Co-organized several local events like TensorFlow Dev Summit 2018 Extended Beijing at Google Beijing Office.
\item Co-developed Flutter's official website in China (flutter-io.cn).
\end{itemize}}

%------------------------------------------------

\entry
{BJMUN (Beijing Model United Nations Association for High School Students)}
{Aug. 2016 -- Aug. 2017}
{\emph{Co-Organizer}
\begin{itemize}
\item Managed the largest MUN association in Beijing (60+ member schools) with 12 other co-organizers.
\item Organized two of the most influential Model UN conferences (each with 500+ participants) for high school students in Beijing.
\item Run the web, email, ns \& git server of the association.
\end{itemize}}

%------------------------------------------------

\entry
{\href{https://chaoli.club}{Chaoli Forum}}
{Nov. 2014 -- May. 2015}
{\emph{Co-Founder \& Developer}
\begin{itemize}
\item Developed functions like documents uploading, CDN integration, customer feedback, etc. based on esoTalk, a no-longer maintained open source forum program, as a member of the initial development team and founding team of Chaoli forum, a forum for Math, Physics, Chemistry, and Informatics enthusiasts, which now has 5,000+ users and 40,000+ threads.
\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	CODING SECTION
%----------------------------------------------------------------------------------------

\section{coding (excerpt)}

\begin{entrylist}

%------------------------------------------------

\entry
{MUNPANEL}
{Group Project - Team Leader}
{\href{https://github.com/MUNPANEL/munpanel_v1}{github.com/MUNPANEL/munpanel\_v1}\\
An all-in-one Model United Nations platform for high school students with 2,000+ registered users\\
Stack: PHP (30,000+ lines), Laravel, MySQL, VMware ESXi, Sentry, etc.
}

%------------------------------------------------

\entry
{MessageOnTap API}
{Part of larger Project, Main Author}
{\href{https://github.com/MessageOnTap/MessageOnTap_API}{github.com/MessageOnTap/MessageOnTap\_API}\\
IPC library, powering plugins for MessageOnTap, a development framework for personal-data-powered messaging assistants.\\
Stack: Java, Android
}

%------------------------------------------------

\entry
{Notes to Keep}
{Personal Project}
{\href{https://github.com/adamyi/notes_to_keep}{github.com/adamyi/notes\_to\_keep}\\
Export Apple iCloud Notes to Google Keep\\
Stack: Python
}

%------------------------------------------------

\entry
{v6dns}
{Personal Project}
{\href{https://github.com/adamyi/v6dns}{github.com/adamyi/v6dns}\\
A DNS Server which enforces local devices to prioritize IPv4 or IPv6.\\
Stack: NodeJS
}

%------------------------------------------------

\entry
{golinks}
{Personal Project}
{\href{https://github.com/adamyi/golinks}{github.com/adamyi/golinks}\\
A Google-like go/ links service integrated with G Suite\\
Stack: Python, GAE (Google App Engine), Cloud Datastore
}

%------------------------------------------------

\entry
{sqlite-parser}
{Personal Project (Fork)}
{\href{https://github.com/adamyi/sqlite-parser}{github.com/adamyi/sqlite-parser}\\
SQLite Parser for C++. Forked from sql-parser to address SQLite specific statements\\
Stack: C++, Bazel
}

%------------------------------------------------

\entry
{AndroidWechatSQLiteDecrypt}
{Personal Project}
{\href{https://github.com/adamyi/AndroidWechatSQLiteDecrypt}{github.com/adamyi/AndroidWechatSQLiteDecrypt}\\
Xposed module and toolchain to decrypt Android Wechat Database \\
Stack: Java, Android
}

%------------------------------------------------

\entry
{CrowdAnnotator}
{Part of larger Project, Main Author}
{\href{https://github.com/adamyi/CrowdAnnotator}{github.com/adamyi/CrowdAnnotator}\\
A general-purpose web-based crowd-sourcing system for text annotation tasks.\\
Stack: Javascript, Python, MySQL
}

%------------------------------------------------

\entry
{COMP6843 ASP Challenge}
{Personal Project}
{\href{https://github.com/adamyi/comp6443_asp_challenge}{github.com/adamyi/comp6443\_asp\_challenge}\\
A vulnerable microservice infrastructure, used as an assignment for students in UNSW COMP6843 (Extended Web App Security), 2019 term 1.\\
Stack: Docker, Python, Golang, PHP
}

%------------------------------------------------

\entry
{Fury of Dracula}
{Group Project (of 2)}
{\href{https://github.com/adamyi/fury_of_dracula}{github.com/adamyi/fury\_of\_dracula}\\
An AI for a game similar to Scotland Yard, the hide-and-seek game. This was the top performer AI in UNSW COMP2521 (Data Structure and Algorithms) (the seeker AI was significantly better performing than the second place).\\
Stack: C
}

%------------------------------------------------

\entry
{SalesSystem}
{Group Project - Team Leader}
{\href{https://git.yiad.am/cs1531-mcdonalds}{git.yiad.am/cs1531-mcdonalds}\\
An online ordering system for an imaginary burger store as uni assignment, but we designed it to be flexible and configurable enough that it can be used as a general-purpose Sales System. We didn't change a single line of code besides configuration for the "requirement changes" as part of the assignment, and got full mark for that assignment.\\
Stack: Python, Docker, MySQL
}

%------------------------------------------------

\end{entrylist}

%------------------------------------------------

\end{document}
